### 2019-11-27 Manuscript/manuscript.tex
add a bit more detail to the geodynamo-plate tectonics discussion point

Another perspective on Proterozoic tectonics, is that the record is one of intermittent subduction \citep{Silver2008a, ONeill2013a}. In such a model, there are extended intervals with a stagnant lid alternating with intervals of differential plate motion. In particular, it was been argued that the Mesoproterozoic Era (1.6 to 1.0 Ga) is an interval when Earth was in a stagnant regime \citep{Silver2008a, ONeill2013a}. The accretionary history of Laurentia following the amalgamation of the Archean provinces is difficult to reconcile with such an interpretation (Figs. \ref{fig:Laurentia_map} and \ref{fig:tectonic_history}). An additional constraint comes from the presence of reliable paleomagnetic poles themselves that are complete with baked contact tests. In a stagnant lid regime, there would not be sufficient heat flow to sustain a geodynamo \citep{Nimmo2000a}. Therefore, the interpretation of stagnant lid for an extended interval implies that Earth should not have had a geomagnetic field that would have enable the preservation of paleomagnetic poles with positive field tests. The record of poles with positive baked contact tests through the Paleoproterozoic and Mesoproterozoic necessitates a geomagnetic field which itself implies operational plate tectonics. This interpretation of a significant persistent geomagnetic field through much of the Proterozoic (with the potential exception of the Ediacaran; \citealp{Bono2019a}) is further bolstered by estimates of paleointensity obtained from mafic dikes from Laurentia (e.g. \citealp{Macouin2006a}) and elsewhere.

>>>>

Another perspective on Proterozoic tectonics, is that the record is one of intermittent subduction \citep{Silver2008a, ONeill2013a}. In such a model, there are extended intervals with a stagnant lid alternating with intervals of differential plate motion. In particular, it has been argued that the Mesoproterozoic Era (1.6 to 1.0 Ga) is an interval when Earth was in a stagnant regime \citep{Silver2008a, ONeill2013a}. The accretionary history of Laurentia following the amalgamation of the Archean provinces is difficult to reconcile with such an interpretation (Figs. \ref{fig:Laurentia_map} and \ref{fig:tectonic_history}). An additional constraint comes from the paleomagnetic record and paleomagnetic poles supported with baked contact tests through the Mesoproterozoic. In a stagnant lid regime, there would not be sufficient heat flow across the core-mantle boundary to is necessary to sustain a geodynamo \citep{Nimmo2000a, Buffett2000b}. Baked contact tests indicate that, at the time of dike emplacement, there was an appreciable field such that both the cooling magma and the heated country rock in the vicinity of a dike were able to acquire a primary coherent magnetization direction. Additionally, since paleomagnetic poles are developed from many individual cooling units across a region, the similarity of the directions across an igneous province indicates that the magnetizations were dominantly acquired from the geomagnetic field rather than being influenced by local variable crustal magnetizations.  Therefore, the record supports the persistence of a geomagnetic field through the Paleoproterozoic and Mesoproterozoic (Table 2) which implies active plate tectonics that enabled sufficient core-mantle boundary heat flow to power the geodynamo.  This interpretation of a significant persistent geomagnetic field through much of the Proterozoic (with the potential exception of the Ediacaran; \citealp{Bono2019a}) is further bolstered by estimates of paleointensity obtained from mafic dikes from Laurentia (e.g. \citealp{Macouin2006a}) and elsewhere.
